Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow

### 2012-02-21 Text/introduction.tex
Made an abstract and introduction.

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient addressing the
following challenges: the flow pattern  depends on the capillary number $Ca$ regime, i.e. for
$Ca<0.7$ the flow has a vortex in front of the
bubble, but for the larger capillary number it hasn't;  the mass sources is comparable of the
representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
media \cite{jos-mass}); the connection between time and space domains for moving bubbles; the
definition of the mass transfer coefficient which is defined through the characteristic
concentration (inlet/outlet concentration, average concentration). The following boundary conditions
were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
simulations. It was shown that the time dependent average concentration to be a characteristic
concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
concentration to be a characteristic concentration produce unreliable results. In comparison, a few
unit cells open boundaries conditions resemble physical situation most and are harder to conduct
but provide the volumetric mass transfer coefficient based only on the spatial information for the
capillary number $Ca>0.7$. As well, a few unit cells simulations can provide more information about
mixing in the liquid slug in comparision with the periodic boundary conditions. We show
that all presented in literature strategies are extreme limits of one equation,
Eq. {\color{red} give equation number here}. Finally, the correlation for different Peclet numbers
is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
comparison. The work is of use to people performing mass transfer numerical simulations for bubble
train flow in microchannels and within the
lattice Boltzmann context.
\end{abstract}

\section{Introduction}
The monolith reactors during last years are getting more attention as alternative to slurry
reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
a liquid medium of equal sized, long in comparison with the height bubbles in microchannels, see
Fig. \ref{fig:benchmark:hydro}. This flow regime
is usually characterized by surface tension dominance over inertia and viscous effects and by
comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
in macroscopic counterparts: such as thin films \cite{bretherton} which can remarkably enhance mass
transfer in the film from gas or wall; the plug flow nature that separates liquid slugs from each
other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
of Bretherton-Taylor bubble train flow: continous flow analyzers, lung openings, chemical reactions
as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
lot of different application references in extensive reviews \cite{kreutzer-overview,
gupta-review,yue-mass}.

Among different applications of microchannel flows, this work is focused on the mass transfer
study from gas to liquid. The good understanding of mass transfer and how it depends on the
parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
manufacture a microchannel with necessary properties to ensure that chemical
reactions are performed in the best manner \cite{bercic}. A number 
  This
configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely
different for different capillary numbers, the bubble occupies the significant part of the unit cell
and the flow can be assumed periodic.

For the bubble train the volumetric mass transfer coefficient correlations are represented as a
function of the diffusion coefficient, slug and bubble lengths, and bubble velocity. For example,
\citet{yue-mass} established an experimental correlation for a bubble train as: 
\begin{equation}
\vol =\frac{2}{d_h} \Bigl(\frac{D
\ububble}{\lbubble+\lslug}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3},
\end{equation}
where $\vol$ is the volumetric mass transfer coefficient, $d_h$ is the hydrodynamic capillary
diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
$\ububble$ is the bubble velocity. This correlation is within $10\%$ accuracy for experimental
results for the following range of
parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
$1.4<\frac{\lbubble}{d_h}<6.3$, slug length $1<\frac{\lslug}{d_h}<3.2$,
hydrodynamic diameter $d_h = 400 \mathrm{\mu m}$.

Other correlations can be found in works of \citet{kreutzer-overview}
and \citet{bercic-mass}. Among a variety of experimental works extensively covered
\cite{yue-mass}, the numerical validations to the best authors' knowledge are sparse. One of the
reasons is that the experimental correlations are established for continous system, i.e. one does
not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
in different places. Thus, numerical simulations require a significant computational
resources to be able to simulate enough number of the unit cells to mimic the continuous picture.
There are some works as how to avoid large scale numerical simulations by performing numerical
simulations for one unit cell. For example, \citet{vanbaten-circular} perform numerical
simulations for one unit cell using periodic boundary conditions and measure the volumetric mass
transfer coefficient as:
\begin{equation}
\label{main:simulation:equation}
k_L a=\frac{\mathrm{Flux}}{\cbubble-\coutlet} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
cell\ volume}},
\end{equation}
where $\coutlet=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$. 
The concentration flux is calculated as the difference between overall
average concentration in the whole domain ($\coverall=\int_{V} C \mathrm{d}V /V$)
at time
$t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
simulations and correlations of \citet{bercic-mass} was good. However, the numerical model only
accounts for circular capillaries and short contact times when the
bubble film is not saturated with tracer. As well, authors took the
approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then derived the
hydrodynamics fields by imposing a free-slip condition at the bubble surface. {\color{red} Give
another numerical work by Kreutzer.}

This work aims at the establishing numerical procedures as to how properly obtain the volumetric
mass transfer coefficient in the range of capillary number $0.1\leq Ca\leq 1.0$, where the
hydrodynamic velocity pattern changes. The details to obtain velocities and bubble shapes can be
found in \cite{kuzmin-binary2d}. Fig. \ref{fig:benchmark:hydro} gives the simplified picture for the
bubble train. Different boundary conditions, i.e. the periodic boundary
conditions, open boundaries conditions will be examined to determine the volumetric mass transfer
coefficient. As well, large scale simulations are performed, which simulate from $4$ to $10$ unit
cells.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
\caption{Simplified sketch of the bubble train motion. Using periodic conditions for the velocity
field is natural, but needs validation for the mass transfer. \label{fig:benchmark:hydro}}
\end{figure}

The comparison of volumetric mass transfer coefficient
correlations with experimental correlations and establishing the Sherwood number as a function of
other non-dimensional parameters is the goal of the future work. However, as an example we will
show that one of the most recent correlations for the volumetric mass transfer coefficient by
\citet{yue-mass} resembles current simulations.

We chose to simulate mass transfer of the bubble train due to different reasons:
\begin{description}
\item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
to the homogenous advection-diffusion equation with the mass source.  Therefore, there is a logical
mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
all velocity pattern details, on the other hand one needs to mimic the continous picture which is
seen in experiments. One of the goals of this work is to establish certain criteria as how to
simulate such problems numerically with the help of the lattice Boltzmann method.
\item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
the reference frame moving with
the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
numbers there is no vortex and stremalines go around the bubble, see Fig.
\ref{fig:streamlines:tweaked:velocity}. Thus, the problem is interesting because of different
hydrodynamic patterns depending on the capillary number which governs a number of experimental
parameters as the slug length, the film thickness and the existence of the vortex in front of the
bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview}. One of the particular goal of
this work is to study mass transfer dependence on the completely different velocity patterns
depending on the capillary number $Ca$. 
\end{description}

@@

The mass transfer problems in the lattice Boltzmann framework were mainly addressed in series of
works of Dr. Ginzburg and co-authors
\cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}. However, all these works
are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
framework. In comparison, this work aims to establish the procedure of how to obtain the
volumetric mass transfer coefficients for bubble train flow. One should mention the work of
\citet{inamuro-scalar-boundary} simulates heat and mass transfers in the porous media and the work
of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While two last works are focused
at the particular mass transfer problems, both problems are of homogenuous nature and do not
guide as how to simulate the non-homogenous problems.

The overall goal of this paper is to address the questions arised and to establish the numerical
procedure suitable to measure the volumetric mass transfer coefficient in the context of the
lattice Boltzmann method. We will utilize the results of numerical simulations of bubble flow
obtained
before \cite{kuzmin-binary2d,kuzmin-binary3d}.

The paper is organized as follows. The mass transfer coefficients and volumetric mass transfer
coefficients definitions are covered. The limiting cases from the continuos representation and their
application to present simulations are given. The mass transfer simulations benchmarks are
presented. Finally, numerical simulations of different boundary conditions and large scale
simulations and comparison between them are presented.

\section{Mass transfer definitions}
By the definition the mass transfer coefficient from the surface with the imposed constant
concentration $\cbubble$ is the following:
\beq
\label{eq:main:definition}
k_L=\frac{\dot{m}}{P \Delta C},
\feq
where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the surrounding medium
$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
$\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at the infinite distance
from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
the medium concentration can be the average concentration in the domain, the flux averaged
concentration at the inlet or outlet. Thus, one needs to establish a thorough definition of the volumetric
mass transfer coefficient in the case of complex geometries and non-trivial hydrodynamic velocity patterns.

There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
theoretical definitions of the mass transfer in case of point mass sources.
\subsection{Point mass sources}
In what follows we will present three approaches to calculate point mass transfer
coefficients:
\begin{enumerate}
\item
Let us look at the infinitesimal small domain of the volume $A \Delta x$ not
moving and with the point mass source. Then the concentration difference can be found as $\Delta C =
\cstar -
C(t)$, where $\cstar$ is the imposed point source concentration, $C(t)$ is
the time dependent average concentration. Therefore one can write the time dependent ODE for the
average concentration in the domain:
\beq
\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (\cstar-C(t)), 
\feq
with the initial condition $C(0)=0$
The solution can be found by solving ODE:
\beq
C(t)= \cstar (1-\exp(-\vol t )), 
\feq
where $\vol$ is the volumetric mass transfer coefficient defined as:
\beq
\vol=k_L \frac{P}{V},
\feq
where $P$ is the source surface, $V$ is the unit cell volume.
\item
The previous consideration is able to predict mass transfer happening in moving with the velocity
$U$ liquid, see Fig. \ref{fig:moving:frame}. 
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
\end{figure}

>>>>

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient addressing the
following challenges: the flow pattern  depends on the capillary number $Ca$ regime, i.e. for
$Ca<0.7$ the flow has a vortex in front of the
bubble \cite{giavedoni-numerical}, but for the larger capillary number it hasn't;  the mass sources are comparable of the
representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
media \cite{jos-mass}); the connection between time and space domains for moving bubbles; the
definition of the mass transfer coefficient which is defined through the characteristic
concentration (inlet/outlet concentration, average concentration). The following boundary conditions
were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
simulations. It was shown that the time dependent average concentration to be a characteristic
concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
concentration to be a characteristic concentration produce unreliable results. In comparison, a few
unit cells open boundaries conditions resemble physical situation most and are harder to conduct
but provide the volumetric mass transfer coefficient based only on the spatial information for the
capillary number $Ca>0.7$. As well, a few unit cells simulations can provide more information about
mixing in the liquid slug in comparision with the periodic boundary conditions. We show
that all presented in literature strategies are extreme limits of one equation,
Eq. {\color{red} give equation number here}. Finally, the correlation for different Peclet numbers
is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
comparison. The work is of use to people performing mass transfer numerical simulations for bubble
train flow in microchannels and within the
lattice Boltzmann context.
\end{abstract}

\section{Introduction}
The monolith reactors during last years are getting more attention as alternative to slurry
reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
a liquid medium of equal sized, long in comparison with the channel height bubbles, see
Fig. \ref{fig:benchmark:hydro}. This flow regime
is usually characterized by surface tension dominance over inertia and viscous effects and by
comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
in macroscopic counterparts: such as thin films \cite{bretherton} can remarkably enhance mass
transfer in the film from a gas or from walls; the plug flow nature that separates liquid slugs from each
other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
lot of different application references in extensive reviews \cite{kreutzer-overview,
gupta-review,yue-mass}.

Among different applications of microchannel flows, this work is focused on the mass transfer
study from gas to liquid. The good understanding of mass transfer and how it depends on the
parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
manufacture a microchannel with necessary properties to ensure that chemical
reactions are performed in the best manner. A lot of experiments \cite{bercic-mass,irandoust,kreutzer-overview} confirm 
a number of parameters involved in mass transfer. 
For example,
\citet{yue-mass} established an experimental correlation for the volumetric mass transfer coefficient for a bubble train as
a function of the diffusion coefficient, slug and bubble lengths, and bubble velocity.  
\begin{equation}
\vol =\frac{2}{d_h} \Bigl(\frac{D
\ububble}{\lbubble+\lslug}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3},
\end{equation}
where $\vol$ is the volumetric mass transfer coefficient, $d_h$ is the hydrodynamic capillary
diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
$\ububble$ is the bubble velocity, $D$ is the diffusiont coefficient. This correlation is within $10\%$ accuracy for experimental
results for the microchannels with rectangular/square crossections for the following range of
parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
$1.4<\frac{\lbubble}{d_h}<6.3$, slug length $1<\frac{\lslug}{d_h}<3.2$,
hydrodynamic diameter $d_h = 400 \mathrm{\mu m}$.

Other correlations can be found in works of \citet{kreutzer-overview}
and \citet{bercic-mass}. However, all of them study only a certain set of parameters but do not provide overall picture. 
For example, in the work of \citet{bercic-mass} the bubble lengths were comparatively large that makes the film saturated
with the tracer. Thus, the volumetric mass transfer coefficient accounts only the mass transfer from the bubble caps. 
One can find other correlations and parameters in  the excellent overview of experimental works \cite{yue-mass}.

The same scarcity for parameters study can be found in numerical simulations. There are a number of reasons, such as 
the decoupling of the mass transfer from the multiphase simulations. Authors \cite{kreutzer-overview,vanbaten-circular} used
the approximations of bubble shapes obtained from experiments and numerical simulations, obtained hydrodynamic fields with 
one-component solver around the approximated bubble shape with the imposed free-slip boundary condition at the surface of the bubble.
After that the tracer concentration is imposed at the bubble surface, and the mass transfer solver is run with the hydrodynamic fields obtained
from the previous step. The main assumption here is the bubble shape approximation. The approximation as two hemispheres and cylinder
\cite{vanbaten-circular} for a bubble shape is good only for small capillary numbers, say $Ca<0.1$ and cannot be used for larger capillary numbers, 
where the bubble shape resembles a bullet shape \cite{kuzmin-binary2d,kuzmin-binary3d}. Therefore, for larger capillary numbers, i.e. $Ca>0.1$, 
the numerical estimations do require obtaining of hydrodynamic fields and bubble shape from multiphase simulations without analytical estimations.

Another challenge that can be seen in numerical simulations is the transition between continuous picture of experiments with a lot of bubbles to the simulation
of one unit cell which is usually performed in mass transfer simulations. The experimental correlations are established for continuous system, i.e. one does
not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
in different places \cite{bercic-mass}. In contrast, numerical simulations avoid a significant computational burden to simulate a number of unit cells 
to mimic the continuous picture but simulate only one unit cell mass transfer. The gap between numerical simulations and experiments results in the inconsistency of the characteristic concentration determination involved in
the volumetric mass transfer definition, Eq. \ref{eq:main:definition}. In experiments the characteristic concentration is taken as the averaged in time location concentration. 
In numerical simulations by \citet{vanbaten-circular}, the characteristic concentration is taken as the averaged in space inlet/outlet concentration. Authors \cite{vanbaten-circular} performed  numerical
simulations for one unit cell using periodic boundary conditions and measured the volumetric mass
transfer coefficient as:
\begin{equation}
\label{main:simulation:equation}
\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\coutlet\rangle} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
cell\ volume}},
\end{equation}
where $\langle\coutlet(t)\rangle=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the averaged in space outlet concentration used as the characteristic concentration in the definition, Eq. \ref{eq:main:definition}. 
The averaged in time concentration flux is calculated as the difference between overall
average concentration in the whole domain ($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$)
at time
$t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass} was good. However, the numerical model only
accounts for circular capillaries and short contact times when the
bubble film is not saturated with tracer. As well, authors took the
approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then obtained
hydrodynamics fields by imposing a free-slip condition at the bubble surface. However, it will be shown later that this strategy is good only for small capillary numbers $Ca<0.1$
where the shape of the bubble is simple. Moreover, the characteristic concentration to be averaged outlet concentration underpredicts the volumetric transfer coefficient for small capillary
numbers $Ca<0.1$ and overpredicts for larger capillary numbers $Ca>0.7$.

Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble train authors feel that they need to examine more carefully the strategies and assumptions which stay behind the mass transfer coefficient numerical simulations measurements. We aim at establishing numerical simulations procedures as to how properly obtain the volumetric
mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions, and address the following situations:
\begin{description}
\item[I] In numerical simulations \cite{vanbaten-circular,kreutzer-overview}, the bubble shape is approximated by two hemispheres and a cylinder which is valid only for the capillary number $Ca\leq 0.1$. It is known \cite{kreutzer-overview} that the liquid slug is well mixed with the concentrator. Due to homogeneity periodic boundary conditions were used, and the averaged in space inlet/outlet concentration as the characteristic concentration was used \cite{vanbaten-circular}. In comparison, we obtain bubble shapes and hydrodynamic fields from multiphase simulations \cite{kuzmin-binary2d,kuzmin-binary3d} and examine different boundary conditions with a few unit cells ($1$ to $10$ unit cells). 
\item[II] The gas holdup, i.e. the ratio of volume occupied by a bubble to an unit cell volume, is
non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
to the homogenous advection-diffusion equation with the mass source \cite{jos-mass}.  Therefore, there is a logical
mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
all velocity pattern details, on the other hand one needs to mimic the continuous picture which is
seen in experiments. Thus, a few unit cells simulations are performed and compared with one unit cell simulations to bridge different scales.
\item[III] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
the reference frame moving with
the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
numbers there is no vortex and streamlines go around the bubble, see Fig.
\ref{fig:streamlines:tweaked:velocity}. Literature results of numerical simulations \cite{kreutzer-overview,vanbaten-circular} are all for $Ca<0.01$.  For non-homogenous situation, i.e. $Ca\geq 0.7$, we want to examine particular questions: whether periodic boundary conditions are valid to calculate the volumetric mass transfer coefficients, whether the change of hydrodynamic pattern significantly changes the way we measure the volumetric mass transfer coefficient (the inlet/outlet averaged in space concentration to be the characteristic concentration).  There is the indication in literature \cite{bercic-mass,yue-mass} of a number of parameters influencing mass transfer, as the slug length, the film thickness. However, to the best authors' knowledge it is not indicated of how the change of the hydrodynamic pattern (capillary number $Ca$ dependency) influence mass transfer. 
\end{description}
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
\caption{Simplified sketch of the bubble train motion. Using periodic conditions for the velocity
field is natural, but needs validation for the mass transfer. \label{fig:benchmark:hydro}}
\end{figure}
Note that the goal of this paper is to establish procedures and boundary conditions used for the volumetric mass transfer coefficient. Though at the end of the manuscript we present comparison of the volumetric mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations \cite{yue-mass}, the thorough
determination of the Sherwood number as a function of
other non-dimensional parameters as gas holdup, bubble/slug lenghts, the capillary number is the goal of the future work.

@@

The mass transfer problems in the lattice Boltzmann framework were mainly addressed in series of
works of Dr. Ginzburg and co-authors
\cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}. However, all these works
are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
framework. In comparison, this work focuses on the application side as to establish the procedure of how to obtain the
volumetric mass transfer coefficients for bubble train flow. One should mention the work of
\citet{inamuro-scalar-boundary} about heat and mass transfers in the porous media and the work
of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While two last works are focused
at the particular mass transfer problems, both problems are of homogeneous nature and do not
guide as how to simulate the non-homogenous problems.

The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
for the bubble train to derive expressions to connect space and time domain. Then the lattice Boltzmann model used to simulate mass transfer is presented followed by benchmarks. Finally, numerical simulations of different boundary conditions and a few unit cells simulations for different hydrodynamic patterns are presented to establish the thorough procedure to determine the volumetric mass transfer coefficient.

\section{Mass transfer definitions}
By the definition the mass transfer coefficient from the surface with the imposed constant
concentration $\cbubble$ is the following:
\beq
\label{eq:main:definition}
k_L=\frac{\dot{m}}{P \Delta C},
\feq
where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the surrounding medium
$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
$\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at the infinite distance
from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
the medium concentration can be the average concentration in the domain or the flux averaged
concentration at the inlet or outlet, etc. Thus, one needs to establish a thorough definition of the volumetric
mass transfer coefficient in the case of complex geometries and non-trivial hydrodynamic velocity patterns.

There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
theoretical definitions of the mass transfer in case of point mass sources.
\subsection{Point mass sources}
In what follows we will present three approaches to calculate point mass transfer
coefficients:
\begin{enumerate}
\item
Let us look at the infinitesimal small domain of the volume $A \Delta x$ not
moving and with the point mass source.  Then the concentration difference can be found as $\Delta C =
\cstar -
C(t)$, where $\cstar$ is the imposed point source concentration, $C(t)$ is
the time dependent concentration, which do not depend on the location due to homogeneity. Therefore, one can write the time dependent ODE for the
concentration in the domain:
\beq
\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (\cstar-C(t)), 
\feq
with the initial condition $C(0)=0$
The solution can be found by solving ODE:
\beq
C(t)= \cstar (1-\exp(-\vol t )), 
\feq
where $\vol$ is the volumetric mass transfer coefficient defined as:
\beq
\vol=k_L \frac{P}{V},
\feq
where $P$ is the source surface, $V$ is the unit cell volume.
\item
The previous consideration is able to predict mass transfer happening in moving with the velocity
$U$ liquid, see Fig. \ref{fig:moving:frame}. 
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
\end{figure}
